\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2019-08-19 icse/eval.tex
Updated evaluation

We found four specification errors in ECMAScript 2020 via \( \tool \).
They were all confirmed by TC39 and will be fixed in the next release.

\paragraph{Ambiguous \textbf{VarScopedDeclarations} for \textit{IterationStatement}}

% test262 결과를 어떻게? 전체 개수 / applicable tests 개수 / succes, fail 개수
% \inred{refactoring for compile rules / get statistics of compile rules}
% 개수만 - stmt / expr / cond / ref 몇개씩? / corner cases 개수
% \inred{proposed language features / related tests in test262 / diff of compile rules}
% 각 feature name / 의미 / compile 성공률 / 결과 test
% \inred{supprot "Assert: ... "?/ confirm found spec errors by TC39}

>>>>

We found four specification errors in ECMAScript 2020 via \( \tool \).
We fixed them and sent pull requests into the official GitHub repository of
ECMAScript specification~\cite{es2020}. They were all confirmed by TC39
and will be fixed in the next release.

First, we found that \textbf{VarScopedDeclarations} syntax-directed algorithms of
specific cases of \textit{IterationStatement} are ambigious.
The \textbf{VarScopedDeclarations} algorithm is used to initially define
the variable declarations before entering speicific scopes. However, the iteration syntax
\( \code{for await (} \; \textit{LeftHandSideExpression} \; \code{of} \;
\textit{AssignmentExpression} \; \code{)} \; \textit{Statement} \)
has two different \textbf{VarScopedDeclarations} algorithms.
In \( \tool \), the spec extractor detects such duplications.

For the \textbf{ExpectedArgumentCount} syntax-directed algorithm, we found that
there are missing cases for some syntax. This algorithm counts the number of
expected arugments of a specific parameters. However, it does not cover all
the cases. For example, if there exists only one formal parameter,
the ECMAScript 2020 specification does not provide any semantics.
We detect this error during evaluations of test262 tests under
the extracted semantics via \( \tool \). It throws an error that there
is no \textbf{ExpectedArgumentCount} algorithm for specific tests.

Moreover, we found an error in \textsf{Ecmarkup}, a toolchain used to specify ECMAScript
and render the raw specification HTML files.
At the first time, we though that we found a missing case for the \textbf{IsFunctionDefinition}
algorithm of unnamed function expressions. However, in the raw specification HTML file,
there are no missing cases. We investigate why it happens and realize that \textsf{Ecmarkup}
itself has a bug to silently remove the {\small opt} subscript in
\( \code{collapsed} \) syntax mode. Thus, unnamed functions are not described
in the rendered HTML file.

\inred{- completion records??}
% The last issue is about the \textit{completion record type}, which is one of controversial features
% in ECMAScript specifications. They are used to describe the propagation of control
% flows and values in abstract algorithms. They are implicitly constructed
% in steps that return values that are not completion records in runtime semantics.
% Moreover, 
% It confuses the type of return values
